Deep Learning does not Replace Bayesian Modeling

### 2021-12-23 DeepLearningAndBayesianSoftware.Rmd
stand alone version of paper

USE_CACHE = TRUE #will have to setup a redis server, strongly recommend doing this
REPORT_PROGRESS = FALSE

@@

```{r DL vs Bayes Graph, echo=FALSE, message=FALSE, warning=FALSE}
library(ggrepel)
year_start <- 2012
year_end <- 2020
years <- year_start:year_end
df <- data.frame(years)

years <- year_start:year_end
scopus.df <- data.frame(years)
#queryM = pkg_query_m
queryM = queryBayVsDeepM
for (i in 1:nrow(queryM)) {
  package_name = queryM[i, 1]
  query = queryM[i, 2]
  for (suffix in c('','_no_comp_sci')) {
#  for (suffix in c('')) {
    year_counts = c()
    for (year in year_start:year_end) {
      url <- paste(BASE_URL, '?query=','REF(', query,')',
                   "+AND+PUBYEAR+=+", year,
                   sep = '')
      if (suffix == '_no_comp_sci') {
        url = paste(url, '+AND+NOT+SUBJAREA(COMP)', sep = '')
      }
      result <- get_results(url)
      json_txt <- rawToChar(as.raw(strtoi(result$content, 16L)))
      data <- jsonlite::fromJSON(json_txt)
      year_counts = c(
        year_counts,
        as.numeric(data$`search-results`$`opensearch:totalResults`))
    }
    scopus.df[paste(
      package_name,
      suffix,
      sep = '')] <- year_counts
  }
}

column_names <- colnames(scopus.df)
col_sums <- colSums(scopus.df)
df_long <- gather(scopus.df, topic, yr_count,
                  column_names[2]:column_names[length(column_names)])

@@

So what is going on here? The next question is what does the the distribution look like for non-computer science subject areas?  Below is a table of subject counts for packages starting in 2006 when PyMC was first released to 2021 with relative percentages listed:

@@

bayesVdeepLearnDf <- getAllSubjectCategories(queryBayVsDeepM)
displayBayesVdeepLearnDf <- makeDisplayTable(bayesVdeepLearnDf)

@@

allDataDf <- cbind(displayBayesVdeepLearnDf,displayDetailDf)
allDataDf <- allDataDf[,c(1,2,3,11,6,7,10,9,4,8,5,12,13)]
displayedColNames <- colnames(allDataDf)
colnames(allDataDf) <- c(displayedColNames[1:12],'detail totals')
kable(allDataDf, booktabs = TRUE) %>% kable_styling(font_size = 10)

>>>>

USE_CACHE = FALSE #will have to setup a redis server, strongly recommend doing this
REPORT_PROGRESS = FALSE
RUN_QUERY <- FALSE #if TRUE will either hit scopus or cache, if false will pull from disk

@@

```{r DL vs Bayes Data Creation, echo=FALSE, message=FALSE, warning=FALSE}
library(ggrepel)
year_start <- 2012
year_end <- 2020
years <- year_start:year_end
df <- data.frame(years)

years <- year_start:year_end

if (RUN_QUERY) {
  scopus.df <- data.frame(years)
  #queryM = pkg_query_m
  queryM = queryBayVsDeepM
  for (i in 1:nrow(queryM)) {
    package_name = queryM[i, 1]
    query = queryM[i, 2]
    for (suffix in c('','_no_comp_sci')) {
  #  for (suffix in c('')) {
      year_counts = c()
      for (year in year_start:year_end) {
        url <- paste(BASE_URL, '?query=','REF(', query,')',
                     "+AND+PUBYEAR+=+", year,
                     sep = '')
        if (suffix == '_no_comp_sci') {
          url = paste(url, '+AND+NOT+SUBJAREA(COMP)', sep = '')
        }
        result <- get_results(url)
        json_txt <- rawToChar(as.raw(strtoi(result$content, 16L)))
        data <- jsonlite::fromJSON(json_txt)
        year_counts = c(
          year_counts,
          as.numeric(data$`search-results`$`opensearch:totalResults`))
      }
      scopus.df[paste(
        package_name,
        suffix,
        sep = '')] <- year_counts
    }
  }

  write.table(scopus.df,"scopus.csv")
}

scopus.df <- NA
scopus.df <- read.table("scopus.csv")
column_names <- colnames(scopus.df)
col_sums <- colSums(scopus.df)
df_long <- gather(scopus.df, topic, yr_count,
                  column_names[2]:column_names[length(column_names)])

@@

So what is going on here? The next question is what does the the distribution look like for non-computer science subject areas?  Below in Table 1 are subject category counts for packages starting in 2006 when PyMC was first released to 2021 with relative percentages listed:

@@

if (RUN_QUERY) {
  bayesVdeepLearnDf <- getAllSubjectCategories(queryBayVsDeepM)
  displayBayesVdeepLearnDf <- makeDisplayTable(bayesVdeepLearnDf)

@@

  allDataDf <- cbind(displayBayesVdeepLearnDf,displayDetailDf)
  allDataDf <- allDataDf[,c(1,2,3,11,6,7,10,9,4,8,5,12,13)]
  write.table(allDataDf,"allDataDf.csv")
}

allDataDf <- read.table("allDataDf.csv")
displayedColNames <- colnames(allDataDf)
colnames(allDataDf) <- c(displayedColNames[1:12],'detail totals')
kable(allDataDf, booktabs = TRUE) %>% kable_styling(font_size = 10)
